\vspace{5cm} \normalsize \textsc{\NetIDb} \\ [2.0cm] \HRule{0.5pt} \\ \LARGE \textbf{\uppercase{\documenttitle}} \HRule{2pt} \\ [0.5cm] \normalsize \textsc{Sergio Castañeiras Morales\\NIU:1598456\\ }\normalsize \vspace*{5\baselineskip}

### 2024-09-10 Manuscript/manuscript.tex
Adding the references file

% Edit these as appropriate
\newcommand\course{}
\newcommand\subject{Final Degree Project}
\newcommand\documenttitle{AI application for azophotoswitches' optimization with pharmacological interest}
\newcommand\hwnumber{1}                  % <-- homework number
\newcommand\NetIDb{Universitat Autònoma de Barcelona}           % <-- NetID of person #2 (Comment this line out for problem sets)

@@

\newpage
\pagestyle{fancyplain}
\headheight 35pt
\lhead{\NetIDb}    
\rhead{\subject}
\rfoot{\small\thepage}
\headsep 1.5em
The current manuscript format is temporal!!!

>>>>

% Edit these as appropriate
\newcommand\course{}
\newcommand\subject{Final Degree Project}
\newcommand\documenttitle{AI application for azophotoswitches' optimization with pharmacological interest}
\newcommand\hwnumber{1} 
\newcommand\NetIDb{Universitat Autònoma de Barcelona}

@@

\newpage
\pagestyle{fancyplain}
\headheight 35pt
\lhead{\NetIDb}    
\rhead{\subject}
\cfoot{}
\rfoot{\small\thepage}
\headsep 1.5em
The current manuscript's format is temporal!!!\par
Testing cite: \cite{NationalLibraryOfMedicineGeneralArticle}

\newpage
%Bibliography %
\bibliographystyle{plain}
\bibliography{references} 
%%%%%%%%
